# (PART) First {-}

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

(ref:cap-nice-fig) Here is a long caption of the figure. **Markdown** can be used in here. [url][url-1] should work and footnotes too. [^footer-1]. Now i ref to chapter \@ref(intro) and definition \@ref(def:money) on what money is.

[^footer-1]: A footnote is here. 

[url-1]: https://bookdown.org/yihui/bookdown/r-markdown.html

```{r nice-fig, fig.cap='(ref:cap-nice-fig)', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
